---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# affinething

The goal of affinething is to provide simple control point georeferencing for un-mapped rasters. 

The main functions are `affinething()` to collect drawn points interactively from an un-mapped raster image and `domath()` to calculate the extent of the raster in geographic terms and `assignproj()` to apply a map projection inline. There are some other experimental functions to write GDAL VRT `gdalvrt()` and to store some known cases for unmapped image sources.  

## Installation

You can install the dev version of affinething from [GitHub](https://CRAN.R-project.org) with:

``` r
devtools::install_github("hypertidy/affinething")
```

## Example

This examples takes an an un-mapped raster and [georefences](https://en.wikipedia.org/wiki/Georeferencing) it by defining some control points for a simple (offset and scale) [affine transformation](https://en.wikipedia.org/wiki/Affine_transformation). 


Generally, we want **diagonal points**, so I tend to think "southwest" and "northeast", it doesn't really matter where they are as long as there's some pixels between them in both directions. Monterey Bay is very recognizable so I read off some long-lat control points using [mapview](https://r-spatial.github.io/mapview/).

```{r example}
library(affinething)
data("montereybay", package = "rayshader")


library(raster)
## we know that rayshader works transpose
r <- t(raster(montereybay))

prj <- "+proj=longlat +datum=WGS84"
## the north tip of Pacific Grove
sw <- c(-121.93348, 36.63674)
## the inlet at Moss Landing
ne <- c(-121.78825, 36.80592)
#mapview::mapview(c(sw[1], ne[1]), c(sw[2], ne[2]), crs = prj)
```


We can obtain raw (graphics) coordinates of those locations from our image, by plotting it and clicking twice with `affinething()`. 

Note the order, the first point is "sw" and the second is "ne" - the order is not important but it must match. 

```{r affine-thing, eval = FALSE}
## mask the raster so we can see easily where we need to click
xy <- affinething(r > 0)
```

In this example the points are 

```{r affine-thing-points}
xy <- structure(c(0.65805655219227, 0.858931100128933, 0.367586425626388, 
0.589597209007295), .Dim = c(2L, 2L), .Dimnames = list(NULL, 
    c("x", "y")))
```
```{r affine-thing2, eval = TRUE, echo = FALSE}
## mask the raster so we can see easily where we need to click
plot(r > 0)
points(xy)
text(xy, lab = 1:2, pos = 4)
```

Now we have everything we need to re-map our raster! We don't need to project our points as the known locations are in the same
coordinate system as the source data. (In other situations we might georeference using a graticule on a projected map.)

```{r affine-remap}
mapped <- assignproj(setExtent(r, domath(rbind(sw, ne), xy, r, proj = NULL)), prj)

m <- rnaturalearth::ne_countries(country = "United States of America", scale = 10)
plot(mapped, col = viridis::viridis(30))
plot(m, add = TRUE)
contour(mapped, levels = -10, lty = 2, add = TRUE)

#mv <- mapview::mapview(mapped)

```




```{r, eval = FALSE, include = FALSE, echo = FALSE}
## Old rough example

r <- raster("dev/www.bom.gov.au/charts_data/IDY20001/current/windarrow/10m/2015-12-21/IDY20001.windarrow-10m.066.png")
a <- regions("windAntarctica")
projection(r) <- a$proj
extent(r) <- a$extent
plot(r)
library(maptools)
data(wrld_simpl)
library(rgdal)
w <- spTransform(wrld_simpl, projection(r))
plot(w, add = TRUE)


ex <- domath(pts, rawxy)
gdalvrt(r, a_ullr = c(xmin(ex), ymax(ex), xmax(ex), ymin(ex)),
        a_srs = "\"+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0\"")


```



Please note that the 'affinething' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
